Title

### 2017-04-21 paper.tex
Cite LITMUS^RT

>>>>

LITMUS\textsuperscript{RT} \cite{LITMUS} is an open source effort for empirically evaluating multiprocessor
real-time scheduling algorithms implemented with Linux. The tested algorithms were compared based on both
raw performance and schedulability (with real overheads considered) assuming either hard or soft real-time
constraints.
